\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-01-12 article.tex
Added more details to the approach section

  The movement number, together with the English description of each movement,
  were registered manually from the condensed encyclopedia. After reviewing
  and making minor corrections to the terminology data, it too was added.

@@

@@

  Supplementing the above with tags containing more information gives us:

@@

  Information about the stance type is presented first, followed by stance
  side (left, right or none where applicable --- ie. sitting stance),
  technique height (low, middle, high), technique side (left arm or right arm,
  can also be both), direction of the technique (when needed), primary
  technique type (attack, block, kick), technique group (punch, strike,
  thrust), tool group (forearm, knife hand, finger etc.), tool (inner forearm,
  outer forearm, double finger etc.), and finally motion type (normal motion,
  slow motion, consecutive motion and so on).

  % FIXME add database and ruby script info here
  % modelled the project in the database (./models)
  %   explain all attributes etc.
  % made a ruby script to parse the text files (link to bootstrap.rb ?)
  %   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
  %   saving the data into an sqlite3 database for analysis
  %

  Classification is done by attaching metadata, in terms of tags, to each
  pattern movement. In most cases, applying tags to movements have been
  straightforward. However, there are movements that need special mention.
  These movements fall into two categories.

>>>>

  The movement number, together with the English description of each movement,
  was registered manually from the condensed encyclopedia. After reviewing and
  making minor corrections to the terminology, it too was added to the
  dataset.

@@

  We then defined the data models with DataMapper, an Object Relational
  Mapper\footnote{\url{http://www.datamapper.org}} (ORM) written in Ruby. The
  models are Ruby classes with properties and associations. Properties define
  field names and data types in the database, whereas the associations defines
  the relationships and cardinality between the models.

  Next we created a Ruby script that reads the dataset and automatically
  populates the database. It sets up associations between models, and adds the
  appropriate tags to every movement, as well as associations between movement
  and pattern.

  Classification is done by attaching metadata, in terms of tags, to each
  pattern movement.

@@

  Supplementing the above with more detailed tags gives us:

@@

  Information about the stance type is presented first, followed by stance
  side (left, right or none where applicable --- for example a sitting
  stance), technique height (low, middle, high), technique side (left arm or
  right arm, it can also be both), direction of the technique (when needed),
  primary technique type (attack, block, kick), technique group (punch,
  strike, thrust), tool group (forearm, knife hand, finger etc.), tool (inner
  forearm, outer forearm, double finger etc.), and finally motion type (normal
  motion, slow motion, consecutive motion and so on).

  In most cases, applying tags to movements have been straightforward.
  However, there are movements that need special mention.  These movements
  fall into two categories.
